### 2018-04-19 experiments.tex
code

@@

Using the original TSTL harness, approxoimately \emph{over 20\%} of all {\tt redis-py}
regression tests (of length 200) generated were flaky.  Using the
nondeterminism checker to reduce flaky tests to a minimal set allows
an engineer to leave an overnight run that will, in 12 hours, produce
a set of minimal flaky tests exposing the sources of
nondeterminism/flakiness.  In this case, the probability of flakiness
is not important, just the possibility, so we let the delta-debugging
create a minimal test with some non-zero (but possibly very small)
observed probability of nondeterminism.

After removing all identified sources of nondeterminism (the {\tt random-} functions, all
expiration-related functionality and {\tt restore} calls with non-zero
lifetimes, and {\tt spop}), but leaving all other suspect funcitonality in
place (e.g. pipes), no flakiness was observed in a sample of over 1,000 length
200 tests.  Moreover, because the removals were limited to acutally
observed sources of flakiness, the code coverage loss was minimal.
Mean branch coverage, for regression tests of length 200 was reduced
by less than 5 branches (a less than 1\% decrease).  Obviously, it is
impossible to test the removed calls, but the overall coverage loss is
both minimal and known, and can be made up for using specially-crafted
tests (for instance, wrapping the problematic calls in a way that does
not check the values, or adding a delay after an expiration to allow
the data to expire).  As a price to pay for the ability to produce
fast-executing high-coverage full regression tests (not just tests for
crashes and unexpected exceptions), this is a very acceptable price.

>>>>

\begin{figure*}
\centering 
\begin{subfigure}{0.67\columnwidth}
\centering
\includegraphics[width=\columnwidth]{redisddmin}
\caption{Standard delta-debugging}
\label{fig:r1}
\end{subfigure}
\begin{subfigure}{0.67\columnwidth}
\centering
\includegraphics[width=\columnwidth]{redisddmin}
\caption{P=0.5, 100 samples}
\label{fig:r2}
\end{subfigure}
\begin{subfigure}{0.67\columnwidth}
\centering
\includegraphics[width=\columnwidth]{redisddmin}
\caption{P=0.5, 10 samples, 10 replications}
\label{fig:r3}
\end{subfigure}
\caption{Delta-debugging of the same test, with different ways of
  handling nondeterministic in the reduction predicate.}
\end{figure*}

@@

Using the original TSTL harness, approximately \emph{over 20\%} of all {\tt redis-py}
regression tests (of length 200) generated were flaky.  Using the
nondeterminism checker to reduce flaky tests to a minimal set allows
us to simply set up an overnight run that will, in 12 hours, produce
a set of minimal flaky tests exposing the sources of
nondeterminism/flakiness.  In this case, the probability of flakiness
is not important, just the possibility, so we let the delta-debugging
create a minimal test with some non-zero (but possibly very small)
observed probability of nondeterminism.

Figures \ref{fig:r1}-\ref{fig:r3} show delta-debugging of a typical
{\tt redis-py} nondeterministic test, originally with 287 steps.  The initial test behave
nondeterministically about half the time.  Figure \ref{fig:r1} shows
that this is a non-monotonic reduction problem, where removing steps
can either increase or decrease the probability of nondeterminism.  At
first, unmodified delta-debugging actually improves the probability of
failure, but eventually it produces a test of length 16 that only behaves
nondeterministically 24\% of the time.  The reduction takes only 38
seconds.  For the purpose of identifying commands leading to
nondeterminism, this is acceptable.  However, if we were actually
debugging a complex nondeterminism bug in Redis itself, we might want
a more reliably nondeterministic test.

After removing all identified sources of nondeterminism (the {\tt random-} functions, all
expiration-related functionality and {\tt restore} calls with non-zero
lifetimes, and {\tt spop}), but leaving all other suspect funcitonality in
place (e.g. pipes), no flakiness was observed in a sample of over 2,000 length
200 tests.  Moreover, because the removals were limited to acutally
observed sources of flakiness, the code coverage loss was minimal.
Mean branch coverage, for regression tests of length 200 was reduced
by less than 5 branches (a less than 1\% decrease).  Obviously, it is
impossible to test the removed calls, but the overall coverage loss is
both minimal and known, and can be made up for using specially-crafted
tests (for instance, wrapping the problematic calls in a way that does
not check the values, or adding a delay after an expiration to allow
the data to expire).  As a price to pay for the ability to produce
fast-executing high-coverage full regression tests (not just tests for
crashes and unexpected exceptions), this is a very acceptable price.
